Designing Turk Experiments for Visual Statistical Inference

### 2013-06-10 paper_turk.tex
Amazon description

>>>>

Human observers were recruited to evaluate the experimental lineups through Amazon Mechanical Turk \cite{turk} or MTurk Web site.  It is an online work place where people from around the world can perform some tasks and get paid. Usually tasks are very simple and no specialized training is required. Being a human is the main requirement. Tasks are designed for anyone to do but some tasks may require that workers satisfy some skill level depending on the recruiters need. The tasks are designed such that it does not take much time to complete. Humans are still better than computers in performing these types of tasks. The the amount of money paid for each task is very small as well.

It is very fast, cheap and reliable to recruit people from MTurk. Thats why it is getting very popular among the researchers who perform human subject experiment. The another benefit is that a very diverse pool of subjects can be recruited which is otherwise very hard to obtain for a study. The researchers can easily filter the workers based on their experimental design, such as recruiting people only from a specific geographical location or a group of people who satisfy certain criteria etc. The recruiter can decide who they pay or not. Workers have to satisfy the task requirement to ensure payment. But at the end it is the recruiter who has the final say. Usually recruiters pay promptly after the task has been done properly and thats why MTurk is very popular among the online job seeker. At any point of time thousands of tasks are available for the thousands of workers around the world.

Because of its convenience it is getting popular for scientific research study as well. In comparison with a lab study \cite{suri:2010} perform the same study using MTurk and demonstrate that their study results are as good as the lab study results even though MTurk study required less time and cost while provided more convenience. \cite{majumder:2013} recruited people from MTurk for their simulation study in estimating the power of visual statistical inference. They have done numerous pilot studies in lab before doing actual MTurk study and found similar results. \cite{mason:2012} explains various features of MTurk and describes how it can be used as part of human behavioral study.

We designed and developed a web site which enables to display the lineups to the observers as per experimental design. The MTurk workers were redirected to the web site and the data were collected, stored automatically into a local database server. Demographic informations such as age group, gender and education levels were also collected. The time taken for each evaluation is computed based on the time the plot was shown and the time the feedback was received. The location of the observer is determined by the ip address of the observer.
